Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Patterns in Australian Spatial Statistics

### 2025-07-15 paper/kobakian-cook-anzjs.tex
small tweaks plus abstract revision

\usepackage{pmboxdraw}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Patterns in Australian Spatial Statistics},
  pdfauthor={Stephanie Kobakian; Dianne Cook},
  pdfkeywords={data visualisation, visual
inference, geospatial, statistical graphics},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{abstract}
The choropleth map display is commonly used for communicating spatial
distributions across geographic areas. However, when choropleths are
used the size of the geographic units will influence the understanding
of the distribution derived by map users. The hexagon tile map is
presented as an alternative display for visualizing population related
distributions effectively. Visual inference is used to measure the power
of the hexagon tile map design, and the choropleth is used as a
comparison. The hexagon tile map display is tested using a distribution
that is directly related to the geography, with values monotonically
increasing from the North-West to South-East areas of Australia. This
study finds in a hexagon tile map lineup the single map that contains a
population related distribution is detected with greater probability
than the same data displayed in a choropleth map. These findings should
encourage map creators to implement alternative displays and consider a
hexagon tile map when presenting spatial distributions of heterogeneous
areas.
\end{abstract}

\keywords{data visualisation; visual inference; geospatial; statistical
graphics}

@@

This study compares the effectiveness of the spatial display, a hexagon
tile map, against the standard, a choropleth map, for communicating
information about disease statistics. The choropleth map is the
traditional method for visualizing aggregated statistics across
administrative boundaries. The hexagon tile map builds on existing
displays, such as the cartogram, and tessellated hexagon displays. A
hexagon tile map forgoes the familiar boundaries, in favor of
representing each geographic unit as an equally sized hexagon, placed
approximately in the correct spatial location. It differs in the relaxed
requirement to have connected hexagons, and allows sparsely located
hexagons. This type of display may be useful for other countries, and
other purposes. The algorithm to construct a hexagon tile map is
available in the R package sugarbag \citep{sugarbag}.

@@

The Australian Cancer Atlas \citep{atlas} is an online interactive web
tool created to explore the burden of cancer on Australian communities.
There are many cancer types to be explored individually or aggregated.
The Australian Cancer Atlas allows users to explore the patterns in the
distributions of cancer statistics over the geographic space of
Australia. It uses a choropleth map display and diverging color scheme
to draw attention to relationships between neighbouring areas. The
hexagon tile map may be a useful alternative display to enhance the
atlas.

The experiment was conducted using the lineup protocol, a visual
inference procedure \citep{BCHLLSW09, GIIV}, that can be used to
objectively test the effectiveness of the two displays \citep{GTPCCD}. A
lineup embeds the data plot among a field of null data plots, and an
independent observer is asked to select the most different plot. It was
shown by \citet{VVSIALM} to be an effective way to conduct a hypothesis
test where a plot is treated as a test statistic, and utilised for this
purpose in numerous studies \citep{FFS, Green2021, LCTV}. If the data
plot is selected it is analogous to a rejection of the null hypothesis
(specifying no structure), and the observed data plot is unlikely to
arise from the null scenario. The work of \citet{VH2016} compares the
lineup protocol to performance on statndard tests of visual ability,
concluding that participants' performance is related to general visual
aptitude, to classification rather than spatial reasoning.

@@

The choropleth map is an effective spatial display if the size of the
geographic units is relatively uniform. This is not the case for most
countries. Size heterogeneity in administrative units is particularly
extreme in Australia: most of the landscape of Australia is sparsely
settled, with the population densely clustered into the narrow coastal
strips. Figure~\ref{fig-thyroid} a shows the choropleth map of thyroid
cancer rates in Australia. The choropleth map focuses attention on the
geography, and for heterogeneously sized areas it presents a biased view
of the population related distribution of the statistic \citep{CBATCC}.
\emph{Land does not get cancer, people do} -- a more effective way to
communicate the spatial distributions of cancer statistics is needed
(sentiment motivated by \citet{monmonier2018how}).

@@

Alternative algorithms make various trade offs between familiar shapes
and representation of geographic units. The non-contiguous cartogram
method \citep{NAC} keeps the shapes of geographic units intact, and
changes the size of the shape. This method disconnects areas creating
empty space on the display losing the continuity of the spatial display
of the statistic. The Dorling cartogram \citep{ACTUC} represents each
unit as a circle, sized according to the value of the statistic. The
neighbour relationships are mostly maintained by how the circles touch.
A similar approach was pioneered by \citet{RSCW}, using rectangles that
tile to align borders of neighbours \citep{CDWCS}. There have been
thorough reviews of the array of methods, as suitable for cancer atlas
displays \citep[e.g.][]{KCR, BCM}, and experiments demonstrating
cartograms to be more effective than choropleth maps \citep{KFIF}.

The hexagon tile map algorithm, automatically matches spatial regions to
their nearest hexagon tile, from a grid of tiles. It has the effect of
spreading out the inner city areas while maintaining the spatial
locations or regions in remote areas. The algorithm is available in the
R package, sugarbag \citep{sugarbag}. Figure~\ref{fig-thyroid} b shows
the hexagon tile map, where the map is coloured from low (blue) to high
(red). The inner city areas have expanded, making it possible to see the
cancer incidence in the small, densely populated areas. Remote regions
are represented by isolated hexagons, which is not ideal, but maintains
the spatial location of these data values. It is of interest to know how
well the spatial distribution patterns are seen from this display, in
comparison to how they are seen from the choropleth.

@@

The primary factor in the experiment is the map type. The secondary
factor is a trend model. Three trend models were developed, one
mirroring a large spatial trend for which the choropleth would be
expected to do well, and two with differing level of inner city hot
spots. These latter two reflect the structure seen in the thyroid cancer
data (Figure~\ref{fig-thyroid}). This produces six treatment levels:

@@

\caption{\label{fig-exp-design}The experimental design used in the
study. Participants are allocated to with group A or B, to evaluate
either the choropleth or hexagon tile map lineup of each simulated data
set. The text `loc' refers to the location of the data plot in the
lineup.}

@@

on each of lineup. These responses are saved after entering.
Participants were expected to click the submit button on the final page.

@@

\caption{\label{tbl-detect-prop}Model estimates for the proportion of
detection in each of the trend models (standard error). Note that
selecting the data plot by chance would produce a detection rate of
0.05.}

@@

The estimated detection proportion from the model fit, computed using
the \texttt{emmeans} package \citep{Lenth2025} are shown in
Table~\ref{tbl-detect-prop}. For the All Cities trend participants were
about three times more likely to detect the cluster pattern with the
hexagon tile map than the choropleth. The Three Cities trend was
practically not detectable in the choropleth map. The dection rates were
more similar for the NW-SE trend, but slightly higher for the hexagon
tile map, which was a surprise. Note that, these detection rates are all
substantially higher than chance, except for the choropleth map on the
Three Cities. For a single evaluation the detection rate of the data
plot selected by chance is \(1/20=0.05\) because the lineups used in
this experiment had 20 plots. When designing an experiment like this it
is important to produce lineups that strike a balance between simple and
hard, so that there is a chance of discovering the effect of interest.
This experiment has managed to do this extremely well, which is a result
of pilot studies, careful null data generation, and power calculations
to determine appropriate sample size.

@@

Figure~\ref{fig-beeswarm} shows horizontally jittered dot plots to
contrast the time taken by participants to evaluate each lineup facetted
by map type and trend model. Each dot is an evaluation. The time taken
to complete an evaluation ranged from fractions of a second to 60
seconds. The average time taken for type of display is shown as a large
coloured dot on each plot, and show there is little difference in the
average time taken to read a lineup made with either a choropleth or
hexagon tile map.

@@

Table~\ref{tbl-reason} summarises the reasons that participants gave for
their choices: ``clusters'' = ``Clusters of colour'', ``trend'' =
``Colour trend across the areas'', ``consistent'' = ``All areas have
similar colours'', ``hotpots'' = ``Big differences between neighbouring
areas'', ``none'' = ``None of these reasons''. These proportions are
computed separately for each trend, map type and whether the participant
detected the data plot. With All Cities and Three Cities, when correct,
participants tended to select `consistent' with the choropleth, and
`clusters' with the hexagon tile map. With the NW-SE trend, `trend' was
primarily selected for the choropleth, but `clusters' was the primary
reason for the hexgon tile map. The primary reasons are similar when the
participant did not detect the data plot.

@@

\caption{\label{tbl-reason}Proportion of participants chose each reason
for their choice of plot, computed separately for each Trend and Map
Type level, and whether the data plot was detected. The primary reason
when participants were evaluating the choropleth map was `consistent' or
`trend', but for the hexagon tile map it was `clusters', when they
detected the data plot.}

@@

Of the 90 participants, 66 were male, and 24 female. Most participants
(55) had a Bachelors degree, 13 had a Masters degree, and the remaining
22 had high school diplomas. The age distribution was 13, 36, 21, 11, 6
for age groups 18-24, 25-34, 35-44, 45-54, 55+, with 3 preferring not to
answer. Only 1 reported having lived in Australia. Note that, the
purpose of reporting these numbers is to illustrate the reasonable
variety of demographic background of participants. However, \$n=\$90 is
insufficient fit a model including this demographic information.
\citet{MHC} (published in 2025 but conducted in 2012) showed that there
is little difference in performance on lineup experiments between
demographic groups. \citet{VH2016} found that visual aptitude for
reading data plots was associated with math skills, but this study was
done on statistical plots of data, not maps. Assessing math ability
requires substantially more data collection, and does not necessarily
correlate with education level.

@@

One of the strengths but weaknesses of the hexagon tile map is that it
is non-contiguous. Large rural areas are represented by isolated
hexagons. This is why we expected that the hexagon tile map might not
work well to detect large-scale spatial trend (``NW-SE''). The primary
reason for producing the non-contiguous display was to preserve
geography sufficiently for the reader to easily recognise the location.
This is a strength, and allows a map of the country to be drawn
underneath the hexagons. It appears to not inhibit reading of the
spatial distribution based on this experiment. However, there is
considerable room for improving the algorithm and exploring some
variations. These might include increasing the size of isolated
hexagons, or collecting multiple hexagons together.

The manner in which hexagons are exploded out from the city centres is
another direction of research. Ideally, the location of the hexagons
should be close to their original location but this is hard to control
and measure. The current algorithm works sequentially to place hexagons,
radially from a provided centre. There are likely better optimisation
procedures that could impve the layout. For reading the spatial
distribution, this is less important, but if the hexagon tile map is
provided to users as an interactive tool, they will want to locate
themselves in the plot. If the hexagon is not close to the true location
it could be disconcerting.

>>>>

\usepackage{pmboxdraw}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Patterns in Australian Spatial Statistics},
  pdfauthor={Stephanie Kobakian; Dianne Cook},
  pdfkeywords={data visualisation, visual
inference, geospatial, statistical graphics, designed experiment},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{abstract}
The choropleth map is a common tool for communicating spatial
distributions across geographic areas. However, the size of geographic
units can distort interpretation, influencing how users perceive the
distribution. A common alternative is the cartogram, which resizes areas
based on population. Yet, in Australia, the stark disparities in
geography and population make cartograms less suitable. This study
explores the hexagon tile map as an alternative. We report results from
a task-based experiment involving human participants, using the lineup
protocol to assess how well hexagon tile maps and choropleths convey
spatial patterns. Three spatial patterns were tested: one reflecting
geography, with values increasing monotonically from the northwest to
southeast of Australia, and two with clustered high concentrations.
Results show that the hexagon tile map outperforms the choropleth. These
findings support the use of alternative map displays and suggest that
hexagon tile maps are effective for visualising spatial distributions in
heterogeneous regions.
\end{abstract}

\keywords{data visualisation; visual inference; geospatial; statistical
graphics; designed experiment}

@@

This study compares the effectiveness of the spatial display, a hexagon
tile map, against the standard, a choropleth map, for communicating
information about disease statistics. The choropleth map is the
traditional method for visualizing aggregated statistics across
administrative boundaries. The hexagon tile map builds on existing
displays, such as the cartogram, and tessellated hexagon displays. A
hexagon tile map forgoes the familiar boundaries, in favour of
representing each geographic unit as an equally sized hexagon, placed
approximately in the correct spatial location. It differs in the relaxed
requirement to have connected hexagons, and allows sparsely located
hexagons. This type of display may be useful for other countries, and
other purposes. The algorithm to construct a hexagon tile map is
available in the R package sugarbag \citep{sugarbag}.

@@

The Australian Cancer Atlas \citep{atlas} is an online interactive web
tool created to explore the burden of cancer on Australian communities.
There are many cancer types to be explored individually or aggregated.
The Australian Cancer Atlas allows users to explore the patterns in the
distributions of cancer statistics over the geographic space of
Australia. It uses a choropleth map display and diverging colour scheme
to draw attention to relationships between neighbouring areas. The
hexagon tile map may be a useful alternative display to enhance the
atlas.

The experiment was conducted using the lineup protocol, a visual
inference procedure \citep{BCHLLSW09, GIIV}, that can be used to
objectively test the effectiveness of the two displays \citep{GTPCCD}. A
lineup embeds the data plot among a field of null data plots, and an
independent observer is asked to select the most different plot. It was
shown by \citet{VVSIALM} to be an effective way to conduct a hypothesis
test where a plot is treated as a test statistic, and utilised for this
purpose in numerous studies \citep{FFS, Green2021, LCTV}. If the data
plot is selected it is analogous to a rejection of the null hypothesis
(specifying no structure), and the observed data plot is unlikely to
arise from the null scenario. The work of \citet{VH2016} compares the
lineup protocol to performance on standard tests of visual ability,
concluding that participants' performance is related to general visual
aptitude, to classification rather than spatial reasoning.

@@

The choropleth map is an effective spatial display if the size of the
geographic units is relatively uniform. This is not the case for most
countries. Size heterogeneity in administrative units is particularly
extreme in Australia: most of the landscape of Australia is sparsely
settled, with the population densely clustered into the narrow coastal
strips. Figure~\ref{fig-thyroid} a shows the choropleth map of thyroid
cancer incidence rates in Australia. The choropleth map focuses
attention on the geography, and for heterogeneously sized areas it
presents a biased view of the population related distribution of the
statistic \citep{CBATCC}. \emph{Land does not get cancer, people do} --
a more effective way to communicate the spatial distributions of cancer
statistics is needed (sentiment motivated by \citet{monmonier2018how}).

@@

Alternative algorithms make various trade-offs between familiar shapes
and representation of geographic units. The non-contiguous cartogram
method \citep{NAC} keeps the shapes of geographic units intact, and
changes the size of the shape. This method disconnects areas creating
empty space on the display losing the continuity of the spatial display
of the statistic. The Dorling cartogram \citep{ACTUC} represents each
unit as a circle, sized according to the value of the statistic. The
neighbour relationships are mostly maintained by how the circles touch.
A similar approach was pioneered by \citet{RSCW}, using rectangles that
tile to align borders of neighbours \citep{CDWCS}. There have been
thorough reviews of the array of methods, as suitable for cancer atlas
displays \citep[e.g.][]{KCR, BCM}, and experiments demonstrating
cartograms to be more effective than choropleth maps \citep{KFIF}.

The hexagon tile map algorithm, automatically matches spatial regions to
their nearest hexagon tile, from a grid of tiles. It has the effect of
spreading out the inner city areas while maintaining the spatial
locations or regions in remote areas. The algorithm is available in the
R package, sugarbag \citep{sugarbag}. Figure~\ref{fig-thyroid} b shows
the hexagon tile map, where the map is coloured from low incidence
(blue) to high (red). The inner city areas have expanded, making it
possible to see the cancer incidence in the small, densely populated
areas. Remote regions are represented by isolated hexagons, which is not
ideal, but maintains the spatial location of these data values. It is of
interest to know how well the spatial distribution patterns are seen
from this display, in comparison to how they are seen from the
choropleth.

@@

The primary factor in the experiment is the map type. The secondary
factor is a trend model. Three trend models were developed, one
mirroring a large spatial trend for which the choropleth would be
expected to do well, and two with differing level of inner city hot
spots. These latter two reflect the structure seen in the thyroid cancer
incidence data (Figure~\ref{fig-thyroid}). This produces six treatment
levels:

@@

\caption{\label{fig-exp-design}The experimental design used in the
study. Participants are allocated to group A or B, to evaluate either
the choropleth or hexagon tile map lineup of each simulated data set.
The text `loc' refers to the location of the data plot in the lineup.}

@@

on each of lineup. These responses are saved after entering.

@@

\caption{\label{tbl-detect-prop}Model estimates for the proportion of
detection in each of the trend models (standard error). Note that
selecting the data plot by chance would produce a detection rate of
0.083, for each lineup.}

@@

The estimated detection proportion from the model fit, computed using
the \texttt{emmeans} package \citep{Lenth2025} are shown in
Table~\ref{tbl-detect-prop}. For the All Cities trend participants were
about three times more likely to detect the cluster pattern with the
hexagon tile map than the choropleth. The Three Cities trend was
practically not detectable in the choropleth map. The detection rates
were more similar for the NW-SE trend, but slightly higher for the
hexagon tile map, which was a surprise. Note that, these detection rates
are all substantially higher than chance, except for the choropleth map
on the Three Cities. For a single evaluation, the detection rate of the
data plot selected by chance is \(1/12=0.083\) because the lineups used
in this experiment had 12 plots. The choice of 12 plots in the lineups
instead of the usual 20, which would have produced the by chance
detection rate of 0.05, is because reading a map is relatively complex,
and pilot studies suggested that 12 was a reasonable cognitive load but
20 was not. When designing an experiment like this it is important to
produce lineups that strike a balance between simple and hard, so that
there is a chance of discovering the effect of interest. This experiment
has managed to do this extremely well, which is a result of pilot
studies, careful null data generation, and power calculations to
determine appropriate sample size.

@@

Figure~\ref{fig-beeswarm} shows horizontally jittered dot plots to
contrast the time taken by participants to evaluate each lineup faceted
by map type and trend model. Each dot is an evaluation. The time taken
to complete an evaluation ranged from fractions of a second to 60
seconds. The average time taken for type of display is shown as a large
coloured dot on each plot, and show there is little difference in the
average time taken to read a lineup made with either a choropleth or
hexagon tile map.

@@

Table~\ref{tbl-reason} summarises the reasons that participants gave for
their choices: ``clusters'' = ``Clusters of colour'', ``trend'' =
``Colour trend across the areas'', ``consistent'' = ``All areas have
similar colours'', ``hotspots'' = ``Big differences between neighbouring
areas'', ``none'' = ``None of these reasons''. These proportions are
computed separately for each trend, map type and whether the participant
detected the data plot. With All Cities and Three Cities, when correct,
participants tended to select `consistent' with the choropleth, and
`clusters' with the hexagon tile map. With the NW-SE trend, `trend' was
primarily selected for the choropleth, but `clusters' was the primary
reason for the hexagon tile map. The primary reasons are similar when
the participant did not detect the data plot.

@@

\caption{\label{tbl-reason}Proportion of reasons provided by
participants for their plot choice, broken down by Trend, Map Type, and
data plot detection. The primary reason when participants were
evaluating the choropleth map was `consistent' or `trend', but for the
hexagon tile map it was `clusters', when they detected the data plot.}

@@

Of the 90 participants, 66 were male, and 24 female. Most participants
(55) had a Bachelors degree, 13 had a Masters degree, and the remaining
22 had high school diplomas. The age distribution was 13, 36, 21, 11, 6
for age groups 18-24, 25-34, 35-44, 45-54, 55+, with 3 preferring not to
answer. Only 1 reported having lived in Australia. Note that, the
purpose of reporting these numbers is to illustrate the reasonable
variety of demographic background of participants. However, \$n=\$90 is
insufficient to fit a model including this demographic information.
\citet{MHC} (published in 2025 but conducted in 2012) showed that there
is little difference in performance on lineup experiments between
demographic groups. \citet{VH2016} found that visual aptitude for
reading data plots was associated with mathematical skills, but this
study was done on statistical plots of data, not maps. Assessing
mathematical ability requires substantially more data collection, and
does not necessarily correlate with education level.

@@

One of the strengths but potential limitations of the hexagon tile map
is that it is non-contiguous; large rural areas are represented by
isolated hexagons. This is why we expected that the hexagon tile map
might not work well to detect large-scale spatial trend (``NW-SE''). The
primary reason for producing the non-contiguous display was to preserve
geography sufficiently for the reader to easily recognise the location.
This is a strength, and allows a map of the country to be drawn
underneath the hexagons. It appears to not inhibit reading of the
spatial distribution based on this experiment. However, there is
considerable room for improving the algorithm and exploring some
variations. These might include increasing the size of isolated
hexagons, or collecting multiple hexagons together.

The manner in which hexagons are exploded out from the city centres is
another direction of research. Ideally, the location of the hexagons
should be close to their original location but this is hard to control
and measure. The current algorithm works sequentially to place hexagons,
radially from a provided centre. There are likely better optimisation
procedures that could improve the layout. For reading the spatial
distribution, this is less important, but if the hexagon tile map is
provided to users as an interactive tool, they will want to locate
themselves in the plot. If the hexagon is not close to the true location
it could be disconcerting.
